% Reconstructed LaTeX Code for the Resume

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

\usepackage{paracol}           % For the sidebar

\ifxetexorluatex
    \setmainfont{RobotoSlab}
    \setsansfont{Lato}
    \renewcommand{\familydefault}{\sfdefault}
\else
    \usepackage[rm]{roboto}
    \usepackage[defaultsans]{lato}
    \renewcommand{\familydefault}{\sfdefault}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{PastelRed}{HTML}{8F0D0D}
% \colorlet{name}{black}
\colorlet{tagline}{PastelRed}
\colorlet{heading}{VividPurple}
\colorlet{headingrule}{VividPurple}
\colorlet{subheading}{PastelRed}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}

% Packages and configurations (based on typical requirements of altacv)
%\usepackage{hyperref}          % For hyperlinks
%\usepackage{graphicx}          % For loading images

\begin{document}

% Define personal data for the header
\name{JEAN-FRANÇOIS ARBOUR}
\tagline{Software Development, Mathematics}

\personalinfo{%
  \email{jf.arbour@gmail.com}
  \phone{(+631) 740-0772}
  \location{New-York, USA}
  \linkedin{Jef808}
  \github{Jef808}
}

\makecvheader % Creates the header

\AtBeginEnvironment{itemize}{\small}

\columnratio{0.6} % Set the ratio of the columns

\begin{paracol}{2}

\cvsection{Work Experience}

\cvevent{Web Developer - Frontend}{Destm Technologies}{March 2023 -- Present}{Remote}
\begin{itemize}
\item \textbf{Description:} Working on the ToryBurch ecommerce website as a
contractor, part of a team responsible for customer interaction
matters. The codebase, devOps and product management
infrastructures are mature, wide in depth, and the team is very active,
engaged and experienced in various complementary domains.
\item \textbf{Role:} I mostly work towards adapting existing features and
frameworks to allow non-critical resources to be dynamically loaded
as users interact with the site. This involves understanding some of
the more technical aspects of frontend development and
benchmarking various performance-related metrics against new
strategies of bundling and serving the source code.
\item \textbf{Technologies:}
  \begin{itemize}
    \item \textbf{React}, \textbf{Redux}, and \textbf{Typescript} during main development
    \item \textbf{Webpack} for module bundling
    \item \textbf{Jest} with \textbf{react-testing-library} for systematic unit testing
    \item \textbf{Adobe Experience Manager} for Content Management System
    \item \textbf{Java} for the backend
    \item \textbf{Selenium Webdriver} with \textbf{Cucumber} for end-to-end testing
  \end{itemize}
\end{itemize}

\divider

\cvevent{Phd Candidate, Teaching Assistant and Lecturer}{Stony Brook University}{Aug 2015 -- Dec 2022}{New York, USA}
\begin{itemize}
\item \textbf{Description:}Each semesters, I served as a teaching assistant and as a
lecturer for most summers. The courses ranged from beginning
undergraduate to graduate level mathematics.

\item \textbf{Skills Gained:}
  \begin{itemize}
    \item Extensive experience in working through complex problems methodically.
    \item Excellent sense of communication, especially in a context of technical exchange between collegues of varied expertize.
    \item Familiarity with geometry libraries, e.g. CGAL and libIGL, along with vizualisation libraries, e.g. matplotlib and d3.js.
  \end{itemize}
\end{itemize}

% Switch to the second column (sidebar)
\switchcolumn

\cvsection{Education}

\cvevent{Ph.D. in Mathematics \hspace{20px} \small{(On hold)}}{Stony Brook University}{Aug 2015 -- Dec 2022 \hspace{8px} Geometric Analysis}{}

My research was in the field of \emph{geometric analysis},
in particular the study of the \emph{Ricci Flow} on geometric objects of higher
dimension. This area of mathematics is
broadly conderned with deriving knowledge
of geometric objects by analyzing certain
\emph{Partial Differential Equations} arising from the
underlying geometric property of the object.
This led me to focus on computational
approaches to solve these abstract
questions, and I eventually decided to move
my efforts entirely to software development
and engineering.

\divider

\cvevent{Masters in Mathematics}{Université du Québec à Montréal}{Aug 2013 -- Jun 2015 \hspace{6px} Differential Geometry}{}
Those two years gave me the chance to start developping the self-confidence and
correct state of mind required to feel comfortable with the frustration and
insecurities arising when tackling new and difficult problems.

\divider

\cvevent{Bachelor in Mathematics}{Université du Québec à Montréal}{Aug 2010 -- May 2013 \hspace{17px} \hspace{26px} GPA: 4.0}{}


\cvsection{Skills \& Tools}

\begin{itemize}
\item \textbf{C/C++:} STL, BGL, Imgui, Eigen, CGAL, Mlpack, Cmake, Catch2, gpg
\item \textbf{Python:} Matplotlib, Numpy, Keras, General scripting
\item \textbf{Javascript:} React, Redux, VueJs, d3, TypeScript, NodeJs
\item \textbf{Web:} Html, CSS, Webpack, Chrome/Firefox Devtools
\item \textbf{Other:} Linux, Bash, Git, LaTeX, Emacs
\end{itemize}

\cvsection{Spoken Languages}

\begin{itemize}
\item French
\item English
\end{itemize}
% Sidebar content (Skills, Languages, etc.) will be included here

\end{paracol}
\end{document}
